%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}

\begin{document}
\header{daniel}{lemon}
       {software developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    Swiss +41763040272
    UK +447852412132
    ~
    \href{mailto:dan@danlemon.com}{dan@danlemon.com}
    \href{http://danlemon.com}{http://danlemon.com}
    \href{http://github.com/dan2k3k4}{github.com/dan2k3k4}
    ~
    Birth: 12th May 1988
    Nationality: British
    Available: Immediately    
  \section{languages}
    English native
    French intermediate
    Bulgarian beginner
  \section{programming}
  Java
    Python, \LaTeX, Android, MySQL, C++, Arduino
  \section{web}
    Drupal, JavaScript, Wordpress, HTML5, CSS, PHP, jQuery
  \section{tools}
    Eclipse, JIRA, Git, Subversion, ant, Maven, jUnit, Swing, cron, SSH.
  \section{operating systems}
    Windows XP/7, Windows Server 2003, Linux (Ubuntu, Scientific Linux CERN 5, and Redhat).
\end{aside}

% \section{personal profile}

% Actively participate in various programming related meet-up groups \& attend numerous events as well as conferences.

\section{key skills}

Enthusiastic \& outgoing with a determined outlook on enhancing software development projects by utilizing agile methodologies with a keen interest in open-source projects.

\textbf{Java} (intermediate): Built my final year project as a educational \textbf{android} game based on CERN that simulated the LHC particle collisions.

Built an \textbf{open-source} GUI based XML-editor that was created from an older tool; re-engineered the previous version to produce PLC (Programmable Logic Controller) code over an NFS network by interacting with a Python script as well as implemented other features like a custom file lock system for the IEPLC project in CERN.

Produced \textbf{open-source modifications} for Call of Duty 4 (PC) within a team of 4; ensuring everything was packed together for regular monthly releases.

\textbf{Javascript}: Currently participating in \href{http://codeyear.com}{Code Year} by completing a new set of Javascript \& jQuery courses each week for a full year.

% agile, open-source, iterative prototyping, networking
% complex networks, social networks, community detection, community structure, overlapping communities, information diffusion, viral marketing, social inference, recommendation, data mining

\section{education}

\begin{entrylist}
  \entry
    {09/2008 – 07/2012}
    {Computer Science, Bachelors of Science (2:1)}
    {Brunel University, London, UK}
    {Completed various JAVA programs ranging from my prototype 2D Android game to a GUI tool that represented how different Sort algorithms function.}
  \entry
    {09/2007 – 07/2008}
    {Foundations of Information Technology}
    {Brunel University, London, UK}
    {Completed a C++ CLI (command-line interface) that demonstrated advanced mathematical functions.}
  \entry
    {09/1999 – 07/2005}
    {A-Levels}
    {Canon Palmer School, London, UK}
    {Specialization in Computing, Mathematics \& Physics. As well as AS-Level in Business Studies \& 10 GSCEs.}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {06/2010 – 07/2011}
    {\href{http://cern.ch}{CERN}, Geneva, Switzerland}
    {Technical Student: Software Developer}
    {Built a JAVA GUI-based XML-editor that interacted with a Python script to produce PLC (programmable logic controller) source code over an NFS network. Involved in all stages of the software development cycle from initial UML designs, to coding, testing and writing the user and technical documentation. Managed tasks and bugs on JIRA, source on SVN, tests built with jUnit and GUI built using Swing, build script via Ant.}
  \entry
    {04/2010 – 06/2010}
    {\href{http://www.circalit.com}{Circalit}, London, UK}
    {Freelance}
    {Updating and integrating different Wordpress plugins. Implementing design changes in PHP as well as updating the layout to include a jQuery slideshow.}
  \entry
    {04/2010 – 05/2010}
    {\href{http://mikamai.com}{Mikamai}, London, UK}
    {Freelance}
    {Updating the company website to include a new portfolio layout using an open-source CMS platform written in Ruby. Also tasked with updating the Wordpress blog layout and integrating Facebook plugins as well as managing the Facebook page to increase brand awareness.}
  \entry
    {09/2009 – 12/2009}
    {\href{http://www.diffiniti.com}{Diffiniti}, London, UK}
    {Freelance}
    {Working with a team of people who specialise in Search Engine Optimization (SEO) for various large clients. Work involved submitting client information to on-line directories, clients involved \href{http://www.sky.com}{Sky} and \href{http://www.autotrader.com}{AutoTrader}.}
\end{entrylist}

\section{volunteer}

\begin{entrylist}
  \entry
    {08/2012 – 08/2012}
    {\href{http://cern.ch}{CERN}, Geneva, Switzerland}
    {Assistant Organizer}
    {Involved in organising, promoting and ensuring the smooth running of the first official CERN Summer Students Webfest, similar to a weekend long hackathon.}
  \entry
    {08/2011 – 08/2011}
    {\href{http://ghni.org}{Global Hope Network International}, Dire Dawa, Ethiopia}
    {Short-Term Team}
    {Spent a week volunteering with some of the world's poorest. Involved in working with building communities between 3 different villages by organising football matches and creating dialogue with the village elders.}
  \entry
    {10/2006 – 05/2007}
    {\href{http://whistler.ca}{Whistler Village Host}, Whistler, BC, Canada}
    {Village Host}
    {Providing way finding assistance to visitors as well as information and history of the village.}
  \entry
    {10/2006 – 12/2006}
    {\href{http://www.artswhistler.com}{Maurice Young Millennium Place}, Whistler, BC, Canada}
    {Doorman}
    {Verifying event tickets on the door as well as helping to set-up or dismantle the theatre stage.}
  \entry
    {11/2006 – 12/2006}
    {\href{http://whistlerfilmfestival.com}{Whistler Film Festival}, Whistler, BC, Canada}
    {Interviewer}
    {Interviewed people and conducted surveys around the village to record peoples' feelings of the festival.}
\end{entrylist}

\section{interests \& activities}

\textbf{Young @ CERN \& Technical Student Social Organizer}; Organised and managed monthly social events for the students working in CERN. This helped to build a community between the students \& improved social interactions.

Participated in \textbf{Start-up Weekend Geneva 2010}, involved with a team that aimed at creating a fashion company by re-using unsold products from large clothing distributors and \textbf{Start-up Weekend Lausanne 2011}, involved in a team that aimed at building a geo-localisation application focused on providing local shopping deals. The Start-up Weekend events focus on building a start-up company from idea to demo over a 56-hour period in one weekend.

\textbf{Assistant Organizer for the Graduate Developer Community}, help to create and schedule new events with the other organizers. Attended various events including an introduction to using Agile methodology.

Member of the \textbf{London Java Community}, attended various different events as well as being a member of several other meet-up groups such as: London Android Group, PHP London Group and Facebook Developers Garage London.

Attended DroidCon 2011, an \textbf{Android developers conference}, TEDxGeneva 2011, LiFT 2011, and participated in open-source start-up events aimed at teaching students how to get started with an open-source project: from how to commit changes; to forking when building new features.

Avid \textbf{snowboarder} and thoroughly enjoy \textbf{travelling}.

\end{document}
